% LaTeX file for resume
% This file uses the resume document class (res.cls)
\documentclass[centered,overlapped]{res}
% the margin option causes section titles to appear to the left of body text
%\textwidth=5.2in % increase textwidth to get smaller right margin
% \topmargin=-0.25in  % start text higher on the page
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage[none]{hyphenat}  % disable automatic hyphenation
\usepackage{newcent}   % uses new century schoolbook postscript font
\voffset=-0.25in
\setlength{\textheight}{11in}
\hoffset=0.0in

\begin{document}

\name{Joshua Matthews}

\address{153 Riveredge Road \\ Tinton Falls, NJ 07724}
\address{josh@jmatthews.us \\ github.com/jmatth}

\begin{resume}

\section{Experience}

{\bf Engineering Intern} \hfill Twilio\\
\textit{May 2014--August 2014} \hfill San Francisco, CA
\begin{itemize} \itemsep -2pt %reduce space between items
    \item Augmented the internal build tools to run builds in isolated
      environments, allowing for increased throughput and eliminating
      multi-tenancy issues.
    \item Began development of a new tool to manage the internal rpm
      repositories when upstream tools proved to be a bottleneck in the
      development process.
    \item Migrated key services from a home-grown legacy configuration
        system to RPMs and Chef.
\end{itemize}

{\bf HackNY Engineering Intern} \hfill Bitly\\
\textit{June 2013--August 2013} \hfill New York, NY
\begin{itemize} \itemsep -2pt %reduce space between items
    \item Developed backend services to process incoming data as part of a new
      analytics product.
    \item Integrated data from a legacy application by adding new API endpoints
      and writing SQL database migrations, allowing for the eventual retirement
      of the application
    \item Part of the HackNY fellowship program.
\end{itemize}

{\bf Student Systems Programmer} \hfill Rutgers Open System Solutions\\
\textit{January 2012--Present} \hfill New Brunswick, NJ
\begin{itemize} \itemsep -2pt %reduce space between items
	\item Part of a team responsible for building and maintaining RPM packages
    used throughout a user community of 70,000 faculty, staff, and students.
	\item Write, debug, and maintain PHP scripts for web-based applications.
  \item Write and maintain shell scripts to automate system administration tasks
    for production servers.
	\item Assess, diagnose, and resolve system and application issues.
\end{itemize}


\section{Education}

Rutgers University - School of Arts and Sciences \hfill New Brunswick, NJ\\
B.S. in Computer Science \hfill Class of 2015 \\
Major GPA: 3.59 \hfill Overall GPA: 3.28


%\section{Activities}
%{\bf Title,} Organization
%\begin{itemize} \itemsep -2pt
%	\item Items here
%\end{itemize}


\section{Projects}

	{\bf ShellGolf}
  \begin{itemize} \itemsep -2pt %reduce space between items
    \item Presents users with challenges to be solved with shell scripting, and
      scores the solutions based on conciseness.
    \item Submitted code is run inside Docker containers for isolation.
    \item Node.js, MongoDB, Docker, RabbitMQ
  \end{itemize}

	{\bf Facebook File System}
  \begin{itemize} \itemsep -2pt %reduce space between items
    \item Models parts of the Facebook Graph API as a UNIX directory structure,
      allowing Facebook interaction through basic command line tools.
    \item Won third place at Facebook Summer of Hack 2013, NY.
    \item C, FUSE
  \end{itemize}

  {\bf EzPrompt.net}
  \begin{itemize} \itemsep -2pt %reduce space between items
    \item Allows users to easily generate customized prompts for GNU Bash via a
      web interface.
    \item Presents preview of the prompt on back or white backrounds, and the
      generated code for the user to place in their config file.
    \item Javascript, jQuery UI
  \end{itemize}

  {\bf LinkTheDots}
  \begin{itemize} \itemsep -2pt %reduce space between items
    \item Shell script for linking configuration files from a git repository
      into a users home directory.
    \item Includes support symlinking or copying, extending with custom
      scripts, submodule support, and automatic updates when the repository is
      updated.
    \item Written completely in GNU Bash for maximum compatibility.
  \end{itemize}


\section{Languages and Technologies}
\noindent
\begin{tabular}{@{} l l}
  \textbf{Programming Languages:} & Python, Ruby, shell scripting, Javascript,
    C, PHP, Java \\
  \textbf{Version Control:} & Git, Subversion \\
\end{tabular}

\end{resume}
\end{document}
